\documentclass{amsbook}

\usepackage{amsmath, amsthm, amssymb, amsfonts}
\usepackage{thmtools}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{float}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{framed}
\usepackage[dvipsnames]{xcolor}
\usepackage{tcolorbox}
\usepackage{mathrsfs}
\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother


\colorlet{LightGray}{White!90!Periwinkle}
\colorlet{LightOrange}{Orange!15}
\colorlet{LightGreen}{Green!15}

\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}

\declaretheoremstyle[name=Theorem,]{thmsty}
\declaretheorem[style=thmsty,numberwithin=section]{theorem}
\tcolorboxenvironment{theorem}{colback=LightGray}

\declaretheoremstyle[name=Lemma,]{lemsty}
\declaretheorem[style=lemsty,numberwithin=section]{lemma}
\tcolorboxenvironment{lemma}{colback=LightGray}

\newenvironment{solution}[1][Solution]{\proof[#1]\renewcommand{\qedsymbol}{$\blacksquare$}}{\endproof}

\theoremstyle{theorem}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{plain}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{corollary}{Corollary}[theorem]

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}[theorem]{Remarks}

\setstretch{1.2}
\geometry{
    textheight=9in,
    textwidth=5.5in,
    top=1in,
    left=1in,
    right=1in,
    headheight=12pt,
    headsep=25pt,
    footskip=30pt
  }

  \newcommand{\Q}{\mathbb Q}
  \newcommand{\Z}{\mathbb Z}
  \newcommand{\F}{\mathbb F}
  \newcommand{\R}{\mathbb R}
  \newcommand{\C}{\mathbb C}
  \newcommand{\PP}{\mathscr P}
  \renewcommand{\P}{\mathbb P}
  \newcommand{\Aut}{\mathrm {Aut}}
  \newcommand{\Gal}{\mathrm {Gal}}
  \newcommand{\GL}{\operatorname{GL}}
  \newcommand{\stab}{\operatorname{Stab}}
  \newcommand{\p}{\mathfrak p}
  \newcommand{\m}{\mathfrak m}
  \renewcommand{\d}{\operatorname d}
  \newcommand{\cbrt}[1]{\sqrt[3]{#1}}





  

% ------------------------------------------------------------------------------

\begin{document}

% ------------------------------------------------------------------------------
% Cover Page and ToC
% ------------------------------------------------------------------------------

\title{ \normalsize \textsc{}
		\\ [2.0cm]
		\HRule{1.5pt} \\
		\LARGE \textbf{\uppercase{Midterm}
		\HRule{2.0pt} \\ [0.6cm] \LARGE{Differential Topology} \vspace*{10\baselineskip}}
		}
\date{}
\author{\textbf{Sudharshan K V} \\ 
		\today}

\maketitle
\chapter*{Problem 1}
Any matrix $A$ for which $A^TDA = D$ must be invertible, as taking determinants shows. Therefore, it suffices to show $\stab(D)$ is a submanifold of $\GL_n(\R)$. We will show this using the preimage theorem. Note that $A^TDA$ is always symmetric due to $D$ being symmetric.\\

Consider the map $F: A \mapsto A^TDA$ from $\GL_n(\R)$ to the set of symmetric matrices. This map is a polynomial map, hence smooth. We will show that $D$ is a regular value for this map. Indeed, at a point $A$, we may compute the derivative of $F$ as follows.

\begin{align*}
  DF_A(B) &= \frac{\d}{\d t} |_{t=0}\left( F(A+tB) - F(A)\right)\\
          &= \frac{\d}{\d t} |_{t=0}\left( t B^TDA + t A^TDB + t^2 B^TDB \right)\\
          &= B^TDA + A^TDB.    
\end{align*}
One can see that the tangent space of symmetric matrices is the subspace of symmetric matrices in $M_n(\R)$. We will show that the image of $DF_A$ is the whole tangent space. \\

Indeed, let $M$ be any symmetric matrix. Choose \[B = D^{-1}(A^T)^{-1} \frac M 2.\] One then computes

\begin{align*}
  DF_A(B) &= B^TDA + A^TDB\\
          &= \frac{M^T} 2 + \frac M 2\\
          &= M.
\end{align*}
Therefore the derivative of $F$ is surjective at all points of $F^{-1}(D)$. By the preimage theorem, $\stab(D) = F^{-1}(D)$ is a submanifold of $\GL_n(\R)$ with dimension $n^2 - \frac{n(n+1)}2 = \frac{n(n-1)}2$, since $\frac{n(n+1)}2$ is the dimension of the space of symmetric matrices. \\

One also computes that $DF_A(D^{-1}(A^T)^{-1}C) = C^T + C$, so the kernel of $DF_A$ is the space of skew symmetric matrices multiplied by $A^TD$ (when identified as a subspaces of $\R^{n^2}$). The kernel of the differential is the tangent space of $\stab (D)$. \\

We exhibit two matrices $D_1, D_2 $ of the same size for which $\stab D_1$ and $\stab D_2$ are not diffeomorphic. Let \[D_1 =
  \begin{pmatrix}
    1& 0\\ 0& 1
  \end{pmatrix}, D_2 =
  \begin{pmatrix}
    1& 0 \\ 0 & -1
  \end{pmatrix}.\]
Then $\stab(D_1) = \{A\in M_2(\R): A^TA = I\}$ is compact, since it is closed and bounded. The boundedness comes from computing $A^TA$, which forces the columns to have norm $1$, bounding all entries of the matrix between $\pm 1$.\\

Let $c,d$ be large positive real numbers such that $d^2 - c^2 = 1$ (note that such choices can be arbitrarily large). Let $a,b$ be the positive real roots of $c^2+1$ and $d^2 - 1$. Then one has the relation \[(c^2 + 1)(d^2 - 1) = c^2d^2,\] so we have
\begin{itemize}
\item $a^2b^2 = c^2d^2$, hence $ab = cd$.
\item $a^2-c^2 = 1$.
\item $b^2 - d^2 = -1$.
\end{itemize}
When $A =
\begin{pmatrix}
  a&b\\c&d
\end{pmatrix}$, one computes using the three listed relations that $A^TD_2A = D_2$. Therefore, $\stab (D_2)$ is an unbounded closed subset of $\R^{n^2}$. In particular, the stabilizer is not compact and is therefore not diffeomorphic to $\stab(D_1)$.
\chapter*{Problem 2}
\section*{(a)}
We will provide a counter example to show that $p$ need not be a regular value of $f$. Let $X$ be the $2$-sphere, \[X = \{(x,y,z) \in \R^3 : x^2 + y^2 + z^2 = 1 \}.\] Let $\pi: \R^3 \to \R$ be the square of the $z$-coordinate map, i.e., $\pi(x,y,z) = z^2$. Let $Y = \R$ (so $n = 1$), and let $f$ be the restriction of $\pi$ to $X$. So $f = \pi i$, where $i:X\to \R^3$ is the inclusion. Let $p = 0$. In this case, $f^{-1}(p)$ is the circle in $X$ along the $xy$ plane, and is therefore a submanifold of positive dimension with codimension $n$. 

Observe that \[D\pi_{x,y,z} =
  \begin{pmatrix}
    0 \\ 0 \\ 2z
  \end{pmatrix}\] in standard coordinates. Therefore, at any point $x\in X$ with $z$-coordinate $0$, one has that $Df_x = Di_x D\pi_x = 0$. In particular, this means that $p = 0$ is not a regular value of $f$.
\section*{(b)}
Since $X$ is compact, one has $f(X)$ bounded. Therefore, if $v$ is a vector in some orthogonal direction of $W$, then for some large real number $c$, $W + cv$ does not meet $f(X)$. In this case, $f^{-1}(W+cv)$ is the empty set which is a submanifold of $X$.

\section*{(c)}
Let $f:X \to \R^n - 0$ miss the origin. Let $\pi: \R^n - 0 \to \R\P^{n-1}$ be the natural map, given by \[\pi(x_1, \dots, x_n) = [x_1:\dots:x_n].\] We will show that $\ell$ is transverse to $f$ if and only if $\pi (\ell)$ is a regular value of $\pi \circ f$. This is similar to how one shows that a ray $r$ is transverse to $f$ iff the direction of $r$ is a regular value in $S^{n-1}$ (in the proof of Jordan Brower Theorem, HW7).

\begin{lemma}
  Let $v = (v_1,\dots, v_n)$ be a vector in $T_p(\R^n - 0)$, where $p = (p_1, \dots, p_n)$. Then, \[D\pi_p(v) = 0 \text{ if and only if there is some } c \in \R, v = cp.\]
\end{lemma}
\begin{proof}
  Assume $p_1 \neq 0$ without losing generality. We do this in the standard chart around $\pi(p)$. The chart around $[p_1:\dots:p_n]$ is $[x_1:\dots:x_n] \mapsto (x_2/x_1, \dots, x_n/x_1)$. In this chart, we compute the derivative map to be \[D\pi_p =
    \frac{1}{p_1}\begin{pmatrix}[c|ccc]
                   -\tfrac{p_2}{p_1} & &&\\
                   \vdots &  & I &\\
                   -\tfrac{p_n}{p_1}&&&
    \end{pmatrix},\] where $I$ is the size $n-1$ identity matrix. Then evaluating at $v$ and setting $c = v_1/x_1$ (which is well-defined), we find that $D\pi_p(v) = 0$ if and only if $v = cp$.
\end{proof}
Consequently, observe that $\pi$ is a submersion and the kernel of $D\pi_p$ is just the line $\ell$ passing through $0$ and $p$. 
\begin{lemma}
  Let $\ell$ be a line through the origin in $\R^n$. Then, $\pi(\ell)$ is a regular value of $\pi\circ f$ if and only if $f$ is transverse to $\ell$. 
\end{lemma}
\begin{proof}
  Let $x$ be a point in $x$ such that $f(x) \in \ell$. Transversality of $\ell$ and $f$ is equivalent to $Df_x(T_xX) + \ell = \R^n$ for all such $x$. Let $T$ be the tangent space of $\R\P^{n-1}$ at $\pi(f(x))$. The condition $Df_x(T_xX) + \ell = \R^n$ implies $D(\pi\circ f)_x(T_xX) = T$, since $\pi$ is a submersion, and $\ell$ is the kernel of $D\pi_{f(x)}$. Conversely, if $D(\pi\circ f)_x(T_xX) = T$ then $Df_x(T_xX) + \ell = \R^n$ for the exact same reason. Furthermore, $f(x) \in \ell$ if and only if $\pi(f(x)) = \pi(\ell)$. So transversality at all such $x$ is equivalent to the regularity of $f(\ell)$. 
\end{proof}

Now we may choose a regular value of $\R\P^{n-1}$ due to Sard's theorem (even when $n = 1$!). This point yields a line in $\R^n$ which is transverse to $f$.
\chapter*{Problem 3}

All spaces we deal with will be locally Euclidean, hence locally path connected. So we will not distinguish path connectedness from connectedness. Let $\dim Y = n$, $\dim X = n-1$. 

\section*{(a)}

We repeat the Jordan Brouwer argument, but modify the proof for non-emptiness of a certain set.\\

Fix a point $z \in Y$ which is not in $X$. Consider the property $\PP$ on $X$ given by \[\PP: \text{ For all neighborhoods $U$ of $x$, there is a path connecting $z$ to some point in $U$ which does not meet $X$}.\] Let $x$ be a point of $X$ which satisfies $\PP$. Choose a chart $U$ around $X$ so that $X\subset Y$ in this chart is locally is $\R^{n-1} \subset \R^n$. Then $U-X$ has two (path) connected components, say $U_1$ and $U_2$. By $\PP$, there is some point in $U-X$ which is path connected to $z$ in $Y-X$. Say this point is in component $U_1$. Then all points of $U_1$ are path connected to $z$ in $Y-X$. For any neighborhood $V$ around any point in $U\cap X$, there is a point in $U_1 \cap V$, so every point of $U\cap X$ possesses property $\PP$. It follows that the subset of points of $X$ which satisfy $\PP$ is open.\\

Now if $x$ is a point which does not satisfy $\PP$, then there must be some open neighborhood $U$ of $x$ for which no point of $U$ is path connected to $z$ in $Y-X$. Taking $U$ itself as the neighborhood, we see that each point of $U\cap X$ does not satisfy property $\PP$. Therefore, the set of points $x$ which do not satisfy $\PP$ is an open set. The property $\PP$ therefore separates the set $X$ into two open complementary sets. Due to connectedness, one of these sets must be empty.\\

Certainly, there is a point in $X$ for which $\PP$ holds. Choose an arbitrary point $x$ and a path $\sigma: [0,1]\to Y$ from $z$ to $x$. Let $t$ be the infimum of the set $\sigma^{-1}(X)$. Since $X$ is closed in $Y$, we see that $\sigma(t) \in X$. So clearly, $t>0$. Let $x' = \sigma(t)$ and $\sigma' = \sigma|_{[0,t]}$. Then for any open $U$ around $x'$, the set $\sigma'^{-1}(U)$ is an open set in $[0,t]$ around $t$. Hence, there is some point $p = \sigma'(t-\epsilon)$ (choose a small $\epsilon$) in $U$ and a path $\sigma|_{[0,t-\epsilon]}$ from $z$ to $p$ which does not intersect $X$. Since $x'$ satisfies $\PP$, we see that all of $X$ satisfies $\PP$. \\

For $x$ in $X$, choose a small chart $U$ around $x$ where $X\subset Y$ in the chart is $\R^{n-1}\subset \R^n$. Then $U-X$ has two connected components. Choose $z_1, z_2$ in different components. For any point $z$ outside $X$, there is some point in $U-X$ connected to $z$ by a path outside $X$. This point is connected (away from $X$) to either $z_1$ or $z_2$ depending on the component of $U-X$ it lies in. So every point $z$ outside $X$ is connected to either $z_1$ or $z_2$ via a path in $Y - X$. There are thus at most two connected components of $Y-X$.

\section*{(b)}

Consider the two points $z_1$ and $z_2$ from (a). In the chart $U$, there is clearly the straight line path (in $\R^n$) from $z_1$ and $z_2$ which intersects $X$ exactly once (and is transverse). Pulling this back via the chart yields an embedding $\sigma:[0,1] \to Y$ from $z_1$ to $z_2$ which is transverse to $X$ and intersects $X$ exactly once. Call this path $C$. Since $Y-X$ has only one component, we may find a different path $\sigma'$ from $z_1$ to $z_2$ which does not intersect $X$. Assume $\sigma'$ is a smooth embedding (injective, immersion): See note at the end of the solution. We use $Y-X$ for $M$.\\

Observe that $C\subset U$. Let $U_1, U_2$ be components of $U-X$ containing $z_1,z_2$ repsectively. Let $t$ be the supremum of $\sigma'^{-1}(C\cap U_1)$ and $z_1' = \sigma'(t)$. Let $s$ be the infimum of $\sigma^{-1}(C\cap U_2 \cup X)$ and let $z_2' = \sigma'(s)$. The points $z_i'$ are well-defined and lie in $C\cap U_i$ since $\sigma'$ misses $X$. We chose these new points to avoid the intersection of the curves. Now $\sigma'' = \sigma'|_{[t,s]}$ is a curve, and $C'$ be the part of $C$ between $z_1'$ and $z_2'$ (so $C'$ intersects $X$ exactly once). If $C''$ is the image of $\sigma''$, then $C'' \cup C'$ is a loop without self-intersection, so it is homeomorphic to $S^1$. We may perturb $C''\cup C'$  relative to $C'$ so that $C'' \cup C'$ is now diffeomorphic to $S^1$. Call this submanifold $Z$ (submanifold, since it is a smooth embedding of $S^1$). Then $Z\cap X$ is only one point and the intersection is transverse at that point, so $I_2(X,Z) = 1$.\\

\textit{Note:} The following are taken for granted.
\begin{theorem}
  If $M$ is Hausdorff, as in the case for manifolds, then $M$ is arc connected if and only if $M$ is path connected.
\end{theorem}
\begin{lemma}
  A topological embedding $[0,1]\to M$ is homotopic to a smooth embedding $[0,1]\to M$.
\end{lemma}

\section*{(c)}
Every compact $1$-dimensional manifold without boundary is diffeomorphic to disjoint copies of $S^1$. There must be only finitely many such copies because of compactness, since each connected component is open. \\

Assume $Y-X$ has two components. Let $Z$ be a connected closed $1$-dimensional submanifold of $Y$. We may perturb $Z$ so that $Z$ is still diffeomorphic to $S^1$ but $Z$ is now also transverse to $X$. We will show that the size of $Z \cap X$ is even. Consider $Z$ as a map $\rho: [0,1] \to Y$, with $\rho(0) = \rho(1) \not \in X$ (From transversality, say.), where $\rho: S^1 \to Y$ is an embedding. Let $t \in [0,1]$ for which $\rho(t) \in X$. In the chart where $X\subset Y$ becomes $\R^{n-1}\subset \R^n$, the transversality condition means that $\rho'(t)$ has non-zero last coordinate. It follows that for all $\epsilon > 0$ small enough, $\rho(t+\epsilon)$ lies in one component, while $\rho(t - \epsilon)$ lies in the other component.\\ 

Let $C_1, C_2$ be the two components of $Y-X$. Let $t_1 < t_2 < \dots < t_n$ be points in $[0,1]$ which correspond to the points in $Z\cap X$ under $\rho$. Between $t_i$ and $t_{i+1}$, $\rho$ takes values in $Y-X$, so it stays in a component. WLOG, assume $\rho(0)$ lies in $C_1$. Then the argument in the above paragraph can be summarized as \[\text{For all $n$, there is some small $\epsilon_n$ such that } \rho(t_n + \epsilon_n) \in C_{n+1}, \rho(t_n-\epsilon_n) \in C_n,\] where $C_i = C_{i\bmod 2}$. However, since $\rho(0) = \rho(1)$, we also have $\rho(t_n+\epsilon_n) \in C_1$, so $C_{n+1} = C_1$, which means $n$ must be even.\\

So for $Z$ diffeomorphic to $S^1$, we have $I_2(X,Z) = 0$. In general, $Z$ is diffeomorphic to a disjoint union of finitely many $S^1$, so $I_2(X,Z)$ is still $0$.
\section*{(d)}

Consider $S^1 = \R\P^1 = [x_0:0:\dots:0:x_{n+1}]$ as a submanifold of $\R\P^{n+1}$. Then at the (only) intersection point $[1:0:\dots:0]$ of $\R\P^1$ and $\R\P^n$, we compute the tangent spaces in the standard chart to be $\R^n \times 0$ and $0\times 0 \times \dots \times \R$ as subspaces of $\R^{n+1}$. Clearly the intersection is transverse and $I_2(\R\P^n, \R\P^1) = 1$. Therefore, $\R\P^n$ does not split $\R\P^{n+1}$ into two components by virtue of (c). \\

Alternatively it is straightforward (from the definition of the chart map) to show that $\R\P^{n+1} = \R^{n+1} \sqcup \R\P^n$, and since $\R^{n+1}$ is connected, the result follows.
\chapter*{Problem 4}

We begin with some relations between the complex and real derivatives of a holomorphic function $f: \C \to \C$. Let $f(z) = u(x,y) + iv(x,y)$ where $z=x+iy$ and $u,v$ are smooth functions $\R^2 \to \R$. The complex derivative of $f$ is \[f'(z) = u_x(x,y) + iv_x(x,y) =v_y(x,y) - i u_y(x,y).\] The real derivative of $f$ is \[Df_{(x,y)} =
  \begin{pmatrix}
    u_x & u_y \\ v_x & u_x
  \end{pmatrix}.\] Therefore, given $f'(z) = \tilde u(x,y)+ i\tilde v(x,y)$, we may write $Df_z =
\begin{pmatrix}
  \tilde u & -\tilde v\\
  \tilde v & \tilde u
\end{pmatrix}$. It follows that $\det Df = |f'(z)|^2$. In particular, the derivative has non-negative determinant. As a consequence, any orientation on a $\C$ obtained from a holomorphic chart must be the standard orientation on $\C$. \\

For $f$ and $f'$ as before, we also compute that for complex $w = x + iy$, \[Df_z(x,y) =
  \begin{pmatrix}
    \tilde u x - \tilde v y \\
    \tilde v x + \tilde u y
  \end{pmatrix} = f'(z)w.
\] A more general is true for any multivariable holomorphic function $F:\C^n \to \C^m$, since $F'(z)$ is a complex-linear approximation of $F$, which is also a real-linear approximation.

\section*{(a)}

Consider the complex transition map between charts $U_0$ and $U_1$. This is given by $(z_1, z_2) \mapsto (\frac 1{z_1}, \frac{z_2}{z_1})$. The complex derivative of this map is $ D\varphi_{(z_1, z_2)} = 
\begin{pmatrix}
  \frac{-1}{z_1^2} & 0 \\
  \star & \frac{1}{z_1}
\end{pmatrix}$. Each entry is a $2\times 2$ real matrix, and the determinant of this transition map is $\det (\frac{-1}{z_1^2}) \det (\frac{1}{z_1})$. Both of these determinants are positive from the earlier discussion. It follows that the transition map has positive determinant. Similarly the other transition maps have positive determinant, and hence we may provide the standard orientation in all charts to get an orientation of $\C\P^2$.

\section*{(b)}
See that $X = \C\P^1$ is orientable due to similar reasons: there is only one transition map whose derivative has positive determinant. $X$ is homotopic to the manifold $X' = \{[z_1:0:z_2]\} \subset \C\P^2$, via the map $f_t([z_1:z_2]) = [z_1: (1-t)z_2: tz_2]$. One calculates the only intersection point of $X,X'$ to be $p = [1:0:0]$. Furthermore, in the standard chart, the tangent spaces $T_pX, T_pX'$ are $\C\times 0, 0\times \C$ respectively (as subspaces of $\C^2$, so we get transversality). Let $e_1, \dots, e_4$ be the standard basis of $\C^2$. This has a positive orientation due to our choice. Orient $X$ such that $e_1, e_2$ is a positive basis of $X$. In the homotopy $X\to X'$, this basis is transformed to the basis $(e_3, e_4)$. Therefore in $T_pX'$ we must give $(e_3, e_4)$ the positive orientation. See that the change of basis matrix $(e_3,e_4,e_1,e_2) \to (e_1,e_2,e_3,e_4)$ has determinant $1$, so \[T_xX'\oplus T_xX = \C^4\] as oriented vector spaces. We must give the intersection point a $+$ orientation.\\

It follows that $I(X,X) = I(X',X) = 1$. Orienting $X$ the other way ($X$ is connected) changes the orientation of $X'$ to the other way, which preserves the orientation of the intersection points.

\section*{(c)}

Suppose we change the orientation on $\C\P^2$ to the negative of the standard orientation on all charts. We keep the orientation on $X$ from before, so $X'$ has the same orientation as before too. The oriented vector space equality now becomes \[T_xX' \oplus T_xX = -\C^4,\] since $(e_3,e_4,e_1,e_2)$ is now a negatively oriented basis in the new orientation on $\C\P^2$. The intersection point gets a $-$ orientation and so $I(X,X) = -1$ in this case.

\section*{(d)}
Let $Z$ be the zero set of the homogeneous polynomial $F([x:y:z]) \mapsto -x^3 + y^3 + z^3$.\\

Observe that $Z$ is a submanifold of $\C\P^2$. Consider the chart around $z \neq 0$. In this chart, $Z$ is the zero set of $-x^3+y^3-1$. Then $F(x,y) = 0$, then $DF = (-3x^2, 3y^2)$ is non-zero. So, as a complex map, $DF$ is surjective, which means it is surjective as a $2\times 4$ real matrix (complex multiplication corresponds to multiplying the real matrices). So $Z$ is a ($1$-dimensional) submanifold in this chart. Taking other charts shows that $Z$ is a submanifold of $\C\P^2$. It is closed because the complement of $Z$ is open in each chart. $Z$ is hence compact. Furthermore, $Z$ is orientable since it is a $1$-dimensional complex manifold, so all transition maps have positive determinant. We may thus consider $I(X,Z)$ (note that $X,Z$ are of complementary dimension). We will orient $Z$ later!\\

Note that $Z\cap X$ is three points: $[1:y:0]$ where $y^3 = 1$. We will show $X$ and $Z$ are transverse at that intersection. All the points lie in the chart around $[1:0:0]$ so we will work in this chart. The tangent space of $\C\P^2$ at $[1:y:0]$ is $\C^2$, and the tangent space of $X$ is $\C \times 0$, with the standard orientation, say. The tangent space to $Z$ at $p = [1:y:z]$ is (complex-) orthogonal to the $\C$-span of $(3y^2, 3z^2)$ (the gradient of $F$). This is a smoothly-varying vector so we may orient $Z$ so that \[\C\cdot (y^2, z^2) \oplus T_pZ = \C^2\] for all $[1:y:z]$ in $Z$. Here, $\C$ and $\C^2$ are given the standard orientation. Importantly, from the discussion before (a), any orientation on $\C$ obtained from a holomorphic chart must agree with the standard orientation. All transition maps in $Z$ are holomorphic, hence have positive determinant derivative. So an orientation in this chart is part of an orientation on all of $Z$.\\

At the intersection points $p=[1:y:0]$, we see that $T_pX = \C \times 0$ with the standard orientation, while $T_pZ = 0\times \C$ oriented such that \[T_pX\oplus T_pZ = \C^4\] as oriented vector spaces. Therefore the intersection is transverse, and each intersection point is given an orientation of $+$. It follows that $I(X,Z) = 3$.

% ------------------------------------------------------------------------------

% ------------------------------------------------------------------------------
% Reference and Cited Works
% ------------------------------------------------------------------------------

% \bibliographystyle{IEEEtran}
% \bibliography{References.bib}

% ------------------------------------------------------------------------------

\end{document}
