\documentclass{amsart}

\usepackage{amsmath,amssymb,amsfonts,amscd}
\usepackage[all,cmtip]{xy}
\usepackage{enumerate}
\usepackage{ amssymb, latexsym, amsmath}
%\setcounter{MaxMatrixCols}{30}%
\usepackage{fullpage}
\usepackage{url}
\usepackage{hyperref}
\usepackage{ marvosym }
\usepackage{quiver}



\numberwithin{equation}{section}

%\usepackage{cjw-latex}

%\providecommand{\U}[1]{\protect\rule{.1in}{.1in}}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{thm}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{criterion}[theorem]{Criterion}
%\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{wildconjecture}[theorem]{Wild Conjecture}


\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{dfn}{Definition}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{question}[theorem]{Question}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{solution}[theorem]{Solution}




\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{remarks}[theorem]{Remarks}
\newtheorem{summary}[theorem]{Summary}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}



\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\newcommand{\Aut}{\operatorname{Aut}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Tor}{\operatorname{Tor}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\osum}{\oplus}
\newcommand{\aff}{\operatorname{Aff}}

\newcommand{\Id}{\operatorname{Id}}
\newcommand{\concat}{(\Id \to \Omega \Sigma)}
\newcommand{\eval}{(\Sigma\Omega \to \Id)}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\g}{\mathfrak{g}}
\newcommand{\n}{\mathfrak{n}}
\newcommand{\h}{\mathfrak{h}}
\newcommand{\p}{\mathfrak{p}}
\newcommand{\q}{\mathfrak{q}}
\newcommand{\m}{\mathfrak{m}}
\newcommand{\e}{\mathfrak{e}}
\newcommand{\f}{\mathfrak{f}}
\newcommand{\V}{\mathscr{V}}
\newcommand{\D}{\mathscr{D}}
\renewcommand{\S}{\mathscr{S}}
\newcommand{\Sch}{\mathscr{C}}
\newcommand{\Y}{\mathscr{Y}}
\renewcommand{\u}{\mathfrak{u}}
\newcommand{\set}[2]{ \left\{ {#1} \, \left| \, {#2} \right\}\right.}
\newcommand{\A}{\mathbb{A}}
\newcommand{\X}{\mathcal{X}}
\renewcommand{\Im}{\operatorname{Im}}
\newcommand{\T}{\mathscr{T}}
\newcommand{\HH}{\mathscr{H}}
\newcommand{\PGL}{\operatorname{PGL}}
\newcommand{\righthookarrow}{\hookrightarrow}
\newcommand{\sign}{\operatorname{sign}}
\renewcommand{\_}[2]{\underbrace{#1}_{#2}}
\renewcommand{\^}[2]{\overbrace{#1}_{#2}}
\newcommand{\curverightarrow}{\curvearrowright}

\newcommand{\z}{\mathfrak{z}}
\renewcommand{\sl}{\mathfrak{sl}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\RP}{\mathbb{RP}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\C}{\mathbb{C}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\Ind}{\operatorname{Ind}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\Orb}{\mathcal{O}}
\renewcommand{\k}{\mbox{\Fontauri k}}
\newcommand{\Ad}{\operatorname{Ad}}
\newcommand{\ad}{\operatorname{ad}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\End}{\operatorname{End}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\Stab}{\mbox{Stab}}
\newcommand{\Lie}{\operatorname{Lie}}
\newcommand{\GL}{\operatorname{GL}}
\newcommand{\SL}{\operatorname{SL}}
\newcommand{\Sp}{\operatorname{Sp}}
\newcommand{\Mp}{\operatorname{Mp}}
\renewcommand{\a}{\mathfrak{a}}
\newcommand{\Wh}{\operatorname{Wh}}
\newcommand{\Span}{\operatorname{Span}}
\newcommand{\WF}{\operatorname{WF}}
\newcommand{\AC}{\operatorname{AC}}
\newcommand{\Lin}{\operatorname{Lin}}
\newcommand{\Diff}{\operatorname{Diff}}
\newcommand{\Gen}{\operatorname{Gen\, Hom}}
\newcommand{\Her}{\operatorname{Her}}
\newcommand{\pivot}{&}
\newcommand{\sgn}{\operatorname{sgn}}
%\newcommand{C^{\infty}}{DS}
\newcommand{\vsp}{{\vspace{0.2in}}}



\title{Homework 11}

\author{Sudharshan K V}
\begin{document}
\maketitle

\section*{Problem 1}
Let $W = Z\times [0,1]$, and let $H: W \to X$ be the homotopy between $f_0, f_1$. Note that since $f_i$ is an embedding for $i=0,1$, one has $\int_{f_i(Z)}\omega = \int_Z f_i^*(\omega).$ Also, the pullback is functorial, so one has $$\int_Z f_i^*(\omega) = (-1)^i\int_{Z\times \{i\}} H^*(\omega).$$ There is a $-1$ factor because the boundary $Z$'s of $W$ have opposite orientation. Since $\omega$ is closed, one has by Stokes' theorem that \[\int_{f_0(Z)} \omega - \int_{f_1(Z)}\omega = \int_W H^*(d\omega) = 0.\] The homotopy invariance of the integral follows. We will use this result multiple times in this problem set.

\section*{Problem 2}

\section*{Problem 3}

\section*{Problem 4}
(a) Let $v = (0,0,1)$. Then at the point $0$, $\omega$ evaluates to the wedge $dx\wedge dz$ and $T_v^*\omega$ evaluates to the wedge $dx\wedge dz +dx\wedge dy$. One also computes $d\omega = dx\wedge dy\wedge dz$, which is non-trivial.\\

(b) Recall from Jordan Brower separation theorem that $S$ is the boundary of some compact manifold $B$. By Stokes' theorem, one has $\int_S \omega = \int_B d\omega$. The translation is a homotopy and $d\omega$ is closed, so we have $\int_B d\omega = \int_{T_v(B)} d\omega$. Since $T_v(S)$ is the boundary of $T_v(B)$, the result follows after another application of Stokes' theorem.

\section*{Problem 5}
Let $h:(-1,1) \to \R$ be a compactly supported function such that $\int_{(-1,1)}h(t)dt = 1$. For instance, we may choose a bump function normalized so that the integral is $1$. We claim that the form $\beta = h(t)dt$ is a Poincare dual for $S^1$.\\

Let $\alpha = f d\theta + gdt$ be a closed form on $X$. First, we observe that \[\int_{S^1\times t} \alpha = \int_{S^1\times t} f(\theta,t)d\theta = \int_0^{2\pi}f(\theta,t)d\theta,\] for any $t\in (-1,1)$. Now, see that for all such $t$, the circles $S^1\times t$ are homotopic. Therefore the integrals of $\alpha$ over these circles are the same. Consequently, $\int_0^{2\pi} f d\theta$ is independent of $t$.\\

By Fubini's theorem, it follows that \[\int_X \alpha \wedge \beta = \int_{-1}^1 h(t)\int_0^{2\pi}f(\theta,t) d\theta dt = \int_0^{2\pi}f(\theta,0)d\theta \times \int_{-1}^1 h(t).\] The last product of integrals equals to $\int_Z \alpha$ due to the choice of $h$.


\section*{Problem 6}
Let $m$ be the unique integer so that $\gamma$ is homotopic to the map $f_m: z\mapsto z^m$. From the proof of Problem 1, we find that \[\int_{S^1} \gamma^*\omega = \int_{S^1} f_m^*\omega.\] But $\omega$ restricted to the unit circle is the form $d\theta$. Pullback of $d\theta$ along $f_m: S^1 \to S^1$ is $md\theta$. It follows that $\int_{S^1}f_m^*\omega = 2\pi m$. Also $m$ is the winding number of $f_m$ which is also the winding number of $\gamma$. The result follows.


\section*{Problem 7}
(a) Let $\alpha, \beta$ be closed. Then $d(\alpha\wedge \beta) = d\alpha \wedge \beta + (-1)^k\alpha\wedge d\beta = 0$. So closed forms wedge to closed forms. Let $d\alpha, d\beta$ be exact forms. Then $d\alpha\wedge d\beta$ is also exact, for \[d(\alpha\wedge d\beta) = d\alpha\wedge d\beta.\] So exact forms wedge to exact forms. The wedge thus descends to cohomology.\\

(b) Consider the map $[\omega] \mapsto \int_X \omega$ for top forms $\omega$. Because of Stokes' theorem, integral of exact top forms on $X$ is zero. Therefore, the map yields a well-defined linear map on the cohomology classes. Combining this with the map from (a), the integration of a wedge is well-defined on cohomology.\\

(c) The $1$-forms on the torus are ($S^1$-function) linear combinations of $dx,dy$, where these forms arise from the usual forms on $\R^2$ as a quotient. Recall that these two forms generate the first dR cohomology group of $T$. The intersection pairing is thus given by $(dx,dy) = \int_T dx \wedge dy = 1$, where we normalize $dx,dy$ so that the integral is $1$. It follows that $(dy,dx) = -1$. The other pairings $(dx,dx)$ and $(dy,dy)$ are both zero.

\end{document}
